Short-term synaptic and neuronal plasticity act in synergy for deviance detection in spiking networks

### 2022-12-09 paper-1/manuscript.tex
Rev sec Results.DD (sample selection)

Having confirmed the presence of deviance detection in our model, we then turned to an ablation approach to try to identify how the two short-term plasticity mechanisms in the model, STD and TA, enabled the networks to learn relevant regularities. Figure \ref{fig3}a shows the responses to target stimulation of a sample network under ablation. With no plasticity, the responses are indistinguishable between sequences, yielding a DDI of 0, and indicating that stimulation did not have any long-lasting effects in membrane voltage or synaptic conductance. With STD only, the response in the dev sequence developed earlier and very slightly larger, yielding a DDI of 0.03. With TA only, the response became noticeably smaller, but the sequences became readily distinguishable, with high dev, intermediate msc, and low std responses, yielding a DDI of 0.19. Finally, in the full model, the dev response stood out more clearly, leaving much smaller msc and std responses and yielding a DDI of 0.4.

>>>>

Having confirmed the presence of deviance detection in our model, we then turned to an ablation approach to try to identify how the two short-term plasticity mechanisms in the model, STD and TA, enabled the networks to learn relevant regularities. In the remainder of the paper, we will proceed to detail the processes leading to deviance detection on a sample network, then confirm the highlighted trends statistically with reference to the full set of 120 networks and stimuli. The sample network was chosen to be roughly representative of the population as follows: We assessed each network's average response to stimulation with A and B in the msc sequence and calculated z-scores with respect to the population. We then focused on networks whose absolute z-score was less than 1 for both A and B responses, and hand-picked a sample that exhibited both an increased DDI in STD+TA over TA only, and positive SSA indices in both STD+TA and TA only conditions.

Figure \ref{fig3}a shows the responses to target stimulation of the sample network under ablation. With no plasticity, the responses are indistinguishable between sequences, yielding a DDI of 0, and indicating that stimulation did not have any long-lasting effects in membrane voltage or synaptic conductance. With STD only, the response in the dev sequence developed earlier and very slightly larger, yielding a DDI of 0.03. With TA only, the response became noticeably smaller, but the sequences became readily distinguishable, with high dev, intermediate msc, and low std responses, yielding a DDI of 0.19. Finally, in the full model, the dev response stood out more clearly, leaving much smaller msc and std responses and yielding a DDI of 0.4.
